---
title: "Analyzing Kaggle Data Science Survey Data-2017"
author: "Anish Singh Walia"
output:
  html_document:
    df_print: paged
---




## AIM 

This is the part 2 of this project.This is a data analytics project for mining analyzing, visualizing the data collected by the Kaggle Data science survey conducted in 2017.



##### 1) Part 2- Will mostly aim at analyzing things such as what is the most preferred tool for implementing Datascience, Most used ML method, learning platform,What language they recommend etc and other more specific answers related to datascience and machine learning given by the survey participants.



###Let's get started


Let's start with the most preferred tool for implementing DS and ML.

```{r message=FALSE, warning=FALSE}
attach(SurveyDf)

table(MLToolNextYearSelect)
tooldf<-as.data.frame(table(MLToolNextYearSelect)) %>% arrange(desc(Freq))
#let's remove missing value
tooldf[1,]<-NA
tooldf<-na.omit(tooldf)
names(tooldf)<-c("Tool","Count")
#now let's plot the data
hchart(tooldf,hcaes(x=Tool,y=Count),type="column",name="Count",color="#9B6ED8") %>%  
  hc_exporting(enabled = TRUE) %>%
  hc_title(text="Barplot of tools used by participants",align="center") %>%
  hc_add_theme(hc_theme_elementary()) 



toptooldf<-na.omit(tooldf) %>% arrange(desc(Count)) %>% top_n(10)
#plotting a funnel chart of top 10 most used tools entered by the users
col <- c("#d35400", "#2980b9", "#2ecc71", "#f1c40f", "#2c3e50", "#7f8c8d","#000004", "#3B0F70", "#8C2981", "#DE4968")

hchart(toptooldf,hcaes(x=Tool,y=Count),type="funnel",name="Count",color=col) %>% 
  hc_exporting(enabled = TRUE) %>%
  hc_title(text="Funnel chart of top 10 most used tools used by survey participants",align="center")






```

-----------------------


###Let's check Top countries uses which tools ?

Let's first make a dataframe which consists of Top 10 particapnt's countries and grouped by the preferred tool entered by them which is then summarized by the total count.

```{r message=FALSE, warning=FALSE}

countryTool<-SurveyDf %>% group_by(MLToolNextYearSelect,Country) %>%
  select(Country,MLToolNextYearSelect) %>% 
  filter(Country %in% countryCount$Var1, MLToolNextYearSelect %in% toptooldf$Tool) %>%
  summarise(total_count=n()) %>%
  arrange(desc(total_count))

```






















