---
title: "Analyzing Kaggle Data Science Survey Data-2017"
author: "Anish Singh Walia"
output:
  html_document:
    df_print: paged
---

## AIM 

This is a data analytics project for mining analyzing, visualizing the data collected by the Kaggle Data science survey conducted in 2017.


### let's get started

#### Importing the dataset in R


```{r,message=FALSE,warning=FALSE}

require(data.table)
require(highcharter)
require(ggplot2)
require(tidyverse)

SurveyDf<-fread("../Datasets/kagglesurvey2017/multipleChoiceResponses.csv") #for faster data reading

```


-------------------


### Exploratory data analysis


##### 1) Part 1- Analyzing country,ethnicity, gender,age,employment status, learning datascience and other related basic features of the survey participants.

Checking the distribution of each variable-
```{r,message=FALSE,warning=FALSE}
attach(SurveyDf)


table(SurveyDf$GenderSelect)

table(SurveyDf$Country)

summary(na.omit(SurveyDf$Age))

table(SurveyDf$EmploymentStatus)


```


Let's visualize the above varibles to understand the distribution better
I will use the _highcharter_ and __ggplot2__ packages.

```{r,fig.height=4,fig.width=10,warning=FALSE,message=FALSE}
#barplot of Gender
hchart(SurveyDf$GenderSelect,type="bar",name="count",color="green") %>%
  hc_exporting(enabled = TRUE) %>%
  hc_title(text="Barplot of gender",align="center") %>%
  hc_add_theme(hc_theme_elementary()) 

#barplot of Emp_status
hchart(SurveyDf$EmploymentStatus,type="bar",name="count",color="red") %>% 
  hc_exporting(enabled = TRUE) %>%
  hc_title(text="Barplot of Employment Status",align="center") %>%
  hc_add_theme(hc_theme_elementary()) 


#barplot of country
hchart(SurveyDf$Country,type="bar",name="Count",color="blue") %>% 
  hc_exporting(enabled = TRUE) %>%
  hc_title(text="Barplot of Country or participants",align="center") %>%
  hc_add_theme(hc_theme_elementary()) 



#treemap of top 10  countries  of participant
countryCount<-as.data.frame(table(SurveyDf$Country)) %>%  top_n(10) 
hchart(countryCount,hcaes(Var1,value=Freq,color=Freq),name="Count of participants",type="treemap") %>%
  hc_exporting(enabled = TRUE) %>%
  hc_title(text="Tree map of top 10 countries of participants",align="center") %>%
  hc_add_theme(hc_theme_elementary()) 



```


So most of the participants were __Male__ and were __full time employed__. Secondly most of the participants are form __USA__ followed by __India__ in the second place.
This shows that people from these countries are very much interested in Data science and its related subfields, also shows large number of people in the field of Datascience.


Let's check the distribution of the ages of participants--




```{r,message=FALSE,warning=FALSE}

#histogram of age of participants
summary(na.omit(SurveyDf$Age))


hchart(na.omit(SurveyDf$Age),name="count",color="orange") %>%
  hc_title(text="Histogram of Ages of the participants",align="center") %>%
  hc_exporting(enabled=TRUE) %>%
  hc_add_theme(hc_theme_elementary())

```

The distribution is somewhat __positively skewed__ as we can notice the slight long tailed histogram which indicates that the *mean(age) > median(age) > mode(age) * values.
From the above histogram the highest count is of participants form __age 20 to 25__. This indicates that most of the students, young job seekers, freshers etc have taken this survey and are interested in Data Science and its related domains.

We can also check this relationship between Age and employment status of the participants using a __Boxplot__.


---------------------------



### Age and Employment status

```{r}
by(Age,EmploymentStatus,summary)

hcboxplot(x= Age , name="Age of participants", var = EmploymentStatus,color="purple",outliers = FALSE) %>%
  hc_title(text="Boxplot of Ages of the participants and their Employment Status",align="center") %>%
  hc_exporting(enabled=TRUE) %>%
  hc_add_theme(hc_theme_elementary()) %>% 
  hc_chart(type="column") #for vertical box plot









```
Hence the above __Boxplot__ can actually tell us about the bi-variate relation and the statistical distribution between Ages and the Employment status of the survey participants. We can notice that the young participants between age of 20-25 are mostly Unemployed, of looking for job opportunities.













































