---
title: "Analyzing Kaggle Data Science Survey Data-2017"
author: "Anish Singh Walia"
output:
  html_document:
    df_print: paged
---

## AIM 

This is a data analytics project for mining analyzing, visualizing the data collected by the Kaggle Data science survey conducted in 2017.


### let's get started

#### Importing the dataset in R


```{r,message=FALSE,warning=FALSE}

require(data.table)
require(highcharter)
require(ggplot2)
require(tidyverse)

SurveyDf<-fread("../Datasets/kagglesurvey2017/multipleChoiceResponses.csv") #for faster data reading

attach(SurveyDf)
```


-------------------


### Exploratory data analysis


##### 1) Part 1- Analyzing country,ethnicity, gender,age,employment status, learning datascience and other related basic features of the survey participants.

Checking the distribution of each variable-
```{r,message=FALSE,warning=FALSE}
attach(SurveyDf)


table(SurveyDf$GenderSelect)

table(SurveyDf$Country)

summary(na.omit(SurveyDf$Age))

table(SurveyDf$EmploymentStatus)


```


Let's visualize the above varibles to understand the distribution better
I will use the _highcharter_ and __ggplot2__ packages.

```{r,fig.height=4,fig.width=10,warning=FALSE,message=FALSE}
#barplot of Gender
hchart(SurveyDf$GenderSelect,type="bar",name="count",color="green") %>%
  hc_exporting(enabled = TRUE) %>%
  hc_title(text="Barplot of gender",align="center") %>%
  hc_add_theme(hc_theme_elementary()) 

#barplot of Emp_status
hchart(SurveyDf$EmploymentStatus,type="bar",name="count",color="red") %>% 
  hc_exporting(enabled = TRUE) %>%
  hc_title(text="Barplot of Employment Status",align="center") %>%
  hc_add_theme(hc_theme_elementary()) 


#barplot of country
hchart(SurveyDf$Country,type="bar",name="Count",color="blue") %>% 
  hc_exporting(enabled = TRUE) %>%
  hc_title(text="Barplot of Country or participants",align="center") %>%
  hc_add_theme(hc_theme_elementary()) 



#treemap of top 10  countries  of participant
countryCount<-as.data.frame(table(SurveyDf$Country)) %>%  top_n(10) 
hchart(countryCount,hcaes(Var1,value=Freq,color=Freq),name="Count of participants",type="treemap") %>%
  hc_exporting(enabled = TRUE) %>%
  hc_title(text="Tree map of top 10 countries of participants",align="center") %>%
  hc_add_theme(hc_theme_elementary()) 



```


So most of the participants were __Male__ and were __full time employed__. Secondly most of the participants are form __USA__ followed by __India__ in the second place.
This shows that people from these countries are very much interested in Data science and its related subfields, also shows large number of people in the field of Datascience.


Let's check the distribution of the ages of participants--




```{r,message=FALSE,warning=FALSE}

#histogram of age of participants
summary(na.omit(SurveyDf$Age))
#mean > median - positively skewed


hchart(na.omit(SurveyDf$Age),name="count",color="orange") %>%
  hc_title(text="Histogram of Ages of the participants",align="center") %>%
  hc_exporting(enabled=TRUE) %>%
  hc_add_theme(hc_theme_elementary())

```

The distribution is somewhat __positively skewed__ as we can notice the slight long tailed histogram which indicates that the *mean(age) > median(age) > mode(age) * values.
From the above histogram the highest count is of participants form __age 20 to 25__. This indicates that most of the students, young job seekers, freshers etc have taken this survey and are interested in Data Science and its related domains.

We can also check this relationship between Age and employment status of the participants using a __Boxplot__.


---------------------------



### Age and Employment status

```{r}
by(Age,EmploymentStatus,summary)

hcboxplot(x= Age , name="Age of participants", var = EmploymentStatus,color="purple",outliers = FALSE) %>%
  hc_title(text="Boxplot of Ages of the participants and their Employment Status",align="center") %>%
  hc_exporting(enabled=TRUE) %>%
  hc_add_theme(hc_theme_elementary()) %>% 
  hc_chart(type="column") #for vertical box plot









```
Hence the above __Boxplot__ can actually tell us about the bi-variate relation and the statistical distribution between Ages and the Employment status of the survey participants. We can notice that the young participants between age of 20-25 are mostly Unemployed, of looking for job opportunities.





---------------------------------


### Let's see how many are students ?

```{r message=FALSE, warning=FALSE}
table(SurveyDf$StudentStatus)#most didn't fill this field

#let's check if participants are learning DS or not
table(SurveyDf$LearningDataScience) #most of them didn't answered this too
hchart(LearningDataScience,name="count",type="column",color="#99FF33") %>%
  hc_title(text="Barplot of Learning Data science field",align="center") %>%
  hc_exporting(enabled=TRUE) %>%
  hc_add_theme(hc_theme_elementary())


```

Hence we can notice that both these variables were not answered by more than 90% of the participants. So there is less scope of interpretting something from these.


------------------------


### Let's see how many are Coders

```{r message=FALSE, warning=FALSE}
table(CodeWriter)
#so Most of them have entered Yes

hchart(CodeWriter,type="column",name="Count",color="#9645FF") %>%
  hc_title(text="Barplot of Number of Coders",align="center") %>%
  hc_exporting(enabled=TRUE) %>%
  hc_add_theme(hc_theme_elementary())


#let's now check which country has most coders

#Making a new dataframe grouped by country and Code wirter variables and summarized by the count of each
codeCountry<-SurveyDf %>% group_by(CodeWriter,Country) %>% 
  select(CodeWriter,Country) %>%
  filter(CodeWriter %in% c("Yes","No")) %>%
  summarize(total=n())
  
#getting top 10 countries and their total coders and non coders
TopCoders<-codeCountry %>% top_n(10) %>% arrange(desc(total))

hchart(TopCoders,type="column",name=c("Do not write code","Code Writers"),hcaes(x=Country,y=total,group=CodeWriter),color=c("black","#FF4040") ) %>%
  hc_title(text="Barplot of Countries grouped by Coder Writers",align="center") %>%
  hc_exporting(enabled=TRUE) %>%
  hc_add_theme(hc_theme_elementary())


```

---------------

### Who all have switched their Carriers and their Current Job titles


```{r message=FALSE, warning=FALSE}

table(CareerSwitcher) #more have changed their jobs than others who haven't

table(CurrentJobTitleSelect)

#let's make a dataframe to plot a barplot
jobdf<-as.data.frame(table(CurrentJobTitleSelect))
jobdf[1,1]<-"Not answered"
jobdf<-na.omit(jobdf)

jobdf %>% arrange(desc(Freq)) %>%   hchart(hcaes(x=CurrentJobTitleSelect,y=Freq),name="Count",color="#751A75",type="column") %>%
  hc_title(text="Barplot of Current Job titles of the participants",align="center") %>%
  hc_exporting(enabled=TRUE) %>%
  hc_add_theme(hc_theme_elementary())


#let's see the trends countrywise

countryJobs<-SurveyDf %>% group_by(Country,CurrentJobTitleSelect) %>%
        filter(Country %in% countryCount$Var1) %>%
        select(Country,CurrentJobTitleSelect) %>%
        summarize(total=n()) %>%
        arrange(desc(total))

countryJobs[1:2,]<-NA
countryJobs<-na.omit(countryJobs)

#making separate countries for comparative plots of Jobs of that country's participants.

#Colors vectors for plotting
USIndJobs<-countryJobs %>% filter(Country %in% c("United States","India"))
colors <- c("#d35400", "#2980b9", "#2ecc71", "#f1c40f", "#2c3e50", "#7f8c8d","#000004", "#3B0F70", "#8C2981", "#DE4968", "#FE9F6D", "#FCFDBF","#ffb3b3","#66ff33","#00b3b3","#4d4dff")

colors2<-c("#d35400", "#2980b9", "#2ecc71", "#f1c40f", "#2c3e50", "#7f8c8d","#000004", "#3B0F70", "#8C2981", "#DE4968", "#FE9F6D", "#FCFDBF","#ffb3b3","#66ff33","#00b3b3","#4d4dff","7D8A16")


hchart(USIndJobs,type="column",hcaes(Country, y=total,group=CurrentJobTitleSelect),color=colors) %>%
  hc_title(text="Barplot of Jobs of Country's participants",align="center") %>%
  hc_exporting(enabled=TRUE) %>%
  hc_add_theme(hc_theme_elementary())



#USA INDIA and RUSSIA-Top 3 countries with maximum response 

JobsMajorCountry<-countryJobs %>% filter(Country %in% c("United States","India","Russia"))

JobsMajorCountry[13,2]<-NA



hchart(na.omit(JobsMajorCountry),type="column",hcaes(Country, y=total,group=CurrentJobTitleSelect),color=colors) %>%
  hc_title(text="Barplot of Jobs of Country's participants",align="center") %>%
  hc_exporting(enabled=TRUE) %>%
  hc_add_theme(hc_theme_elementary())


```

The above plot shows the comparative current job titles of survey participants form India and USA. 

1)From India Most of the participants were __*Software developers followed by Data scientists*__.

2)From USA most of the participants were *__Data scientists followed by software developers__*.




------------------------------------------


### Let's check the where the participants were Employed?

I will make a dataframe with only top 15 employers type.
```{r}
#finding the top 15 employers type
Employer<-as.data.frame(table(CurrentEmployerType)) %>% top_n(15) %>% arrange(desc(Freq))
Employer[1,]<-NA
names(Employer)<-c("EmployerType","Count")
hchart(na.omit(Employer),type="column",hcaes(x=EmployerType,y=Count),color="#0E2E93") %>%
  hc_title(text="Barplot of top 15 Type of Employers",align="center") %>%
  hc_exporting(enabled=TRUE) %>%
  hc_add_theme(hc_theme_elementary())



EmployerType<-as.data.frame(table(CurrentEmployerType,Country)) %>% top_n(20) %>% arrange(desc(Freq))

#assigning NA values to missing ones
EmployerType[c(1,2,8,12,13,16,19,20),1]<-NA

colnames(EmployerType)<-c("EmployerType","Country","Count")

#plotting data
hchart(na.omit(EmployerType),type="column",hcaes(x=EmployerType, y=Count,group=Country),color=c("#DE4968","#f1c40f","black")) %>%
  hc_title(text="Barplot of Type of Employer and Country",align="center") %>%
  hc_exporting(enabled=TRUE) %>%
  hc_add_theme(hc_theme_elementary())




```






























