---
title: "Analyzing Kaggle Data Science Survey Data-2017:PART-3"
author: "Anish Singh Walia"
output:
  html_document:
    df_print: paged
---


```{r,echo=FALSE,results='hide' ,message=FALSE, warning=FALSE, r,echo=FALSE, results='hide'}
require(data.table)
require(highcharter)
require(ggplot2)
require(tidyverse)

SurveyDf<-fread("../Datasets/kagglesurvey2017/multipleChoiceResponses.csv") #for faster data reading

attach(SurveyDf)
```




## AIM 

This is the part 3 of this project.This is a data analytics project for mining analyzing, visualizing the data collected by the Kaggle Data science survey conducted in 2017.



> Part 3 - This section will analyze and study the professional lives of the participants, their major degree ,time spend studying data science topics, what job titles they hold,which ML method they actually use in the industries , which bolgs the participants prefer the most for studying data science etc.



###Let's get started.

1) Let's start with the most preferred blog sites for learning datascience-This is a multiple answer field. Let's find the top 15 most preferred answers.

```{r message=FALSE, warning=FALSE}

blogs<-SurveyDf %>% group_by(BlogsPodcastsNewslettersSelect) %>%
  summarise(count=n()) %>% 
  top_n(15) %>% 
  arrange(desc(count))

#removing NA value
blogs[1,1]<-NA
colnames(blogs)<-c("Blogname","Count")

#let's plot them
hchart(na.omit(blogs),hcaes(x=Blogname,y=Count),type="column",color="#062D67") %>% 
  hc_exporting(enabled = TRUE) %>%
  hc_title(text="Barplot of most preferred blogs for learning",align="center") %>%
  hc_add_theme(hc_theme_elementary()) 



```
hence one can see that one of the most famous and preferred blog sites are __R bloggers and Kdnuggets__.



----------------------------

2) Let's now study how long aprticipants have been learning data science-

```{r message=FALSE, warning=FALSE}
table(LearningDataScienceTime)

hchart(SurveyDf$LearningDataScienceTime,type="pie",name="count")

```

So most of the participants have started learning data science in the past year itself or its been less than a year since they started studying learning data science.


Let's check the age distribution of the particpiants and for how long they have been learning data science.

```{r}

hcboxplot(x=SurveyDf$Age,var=SurveyDf$LearningDataScienceTime,outliers = F,color="#09870D",name="Age Distribution") %>%
hc_chart(type="column")  %>% 
  hc_exporting(enabled = TRUE) %>%
  hc_title(text="Boxplot of ages and the learning time of participants",align="center") %>%
  hc_add_theme(hc_theme_elementary()) 

```

The above plot was quiet predictable as people with less time learning data science are younger.



---------------------------

### 3) Let's now study what participants entered and feel which skills are important for becoming a data scientist?


Let's do some data wrangling and transformations.

Making a separate data frame for each variable, for easier understanding.
```{r message=FALSE, warning=FALSE}
#let's make a function to ease things
#function takes argument as a dataframe and the categorical variable which we want summarize and group
aggr<-function(df,var) 
{
  require(dplyr)
  var <- enquo(var) #quoting
  dfname<-df %>% 
    group_by_at(vars(!!var)) %>%  ## Group by variables selected by name:
    summarise(count=n()) %>%
    arrange(desc(count))
 
    dfname#function returns a summarized dataframe
  
}

RSkill<-aggr(SurveyDf,JobSkillImportanceR)
RSkill[1,]<-NA
SqlSkill<-aggr(SurveyDf,JobSkillImportanceSQL)
SqlSkill[1,]<-NA
PythonSkill<-aggr(SurveyDf,JobSkillImportancePython)
PythonSkill[1,]<-NA
BigDataSkill<-aggr(SurveyDf,JobSkillImportanceBigData)
BigDataSkill[1,]<-NA
StatsSkill<-aggr(SurveyDf,JobSkillImportanceStats)
StatsSkill[1,]<-NA
DegreeSkill<-aggr(SurveyDf,JobSkillImportanceDegree)
DegreeSkill[1,]<-NA
EnterToolsSkill<-aggr(SurveyDf,JobSkillImportanceEnterpriseTools)
EnterToolsSkill[1,]<-NA
MOOCSkill<-aggr(SurveyDf,JobSkillImportanceMOOC)
MOOCSkill[1,]<-NA
DataVisSkill<-aggr(SurveyDf,JobSkillImportanceVisualizations)
DataVisSkill[1,]<-NA
KaggleRankSkill<-aggr(SurveyDf,JobSkillImportanceKaggleRanking)
KaggleRankSkill[1,]<-NA


hchart(na.omit(RSkill),hcaes(x=JobSkillImportanceR,y=count),type="pie",name="Count") %>% 
  hc_exporting(enabled = TRUE) %>%
  hc_title(text="Piechart of importance of R skill",align="center") %>%
  hc_add_theme(hc_theme_elementary())


hchart(na.omit(PythonSkill),hcaes(x=JobSkillImportancePython,y=count),type="pie",name="Count") %>%
hc_exporting(enabled = TRUE) %>%
  hc_title(text="Piechart of importance of Python skill",align="center") %>%
  hc_add_theme(hc_theme_elementary())

hchart(na.omit(SqlSkill),hcaes(x=JobSkillImportanceSQL,y=count),type="pie",name="Count") %>% 
  hc_exporting(enabled = TRUE) %>%
  hc_title(text="Piechart of importance of SQL skill",align="center") %>%
  hc_add_theme(hc_theme_elementary())

hchart(na.omit(BigDataSkill),hcaes(x=JobSkillImportanceBigData,y=count),type="pie",name="Count") %>% 
  hc_exporting(enabled = TRUE) %>%
  hc_title(text="Piechart of importance of Big Data skill",align="center") %>%
  hc_add_theme(hc_theme_elementary())

hchart(na.omit(StatsSkill),hcaes(x=JobSkillImportanceStats,y=count),type="pie",name="Count") %>% 
  hc_exporting(enabled = TRUE) %>%
  hc_title(text="Piechart of importance of Statistics kill",align="center") %>%
  hc_add_theme(hc_theme_elementary())

hchart(na.omit(DataVisSkill),hcaes(x=JobSkillImportanceVisualizations,y=count),type="pie",name="Count") %>% 
  hc_exporting(enabled = TRUE) %>%
  hc_title(text="Piechart of importance of Data Viz skill",align="center") %>%
  hc_add_theme(hc_theme_elementary())

hchart(na.omit(DegreeSkill),hcaes(x=JobSkillImportanceDegree,y=count),type="pie",name="Count") %>% 
  hc_exporting(enabled = TRUE) %>%
  hc_title(text="Piechart of importance of Degree",align="center") %>%
  hc_add_theme(hc_theme_elementary())

hchart(na.omit(EnterToolsSkill),hcaes(x=JobSkillImportanceEnterpriseTools,y=count),type="pie",name="Count") %>% 
  hc_exporting(enabled = TRUE) %>%
  hc_title(text="Piechart of importance of Enterprise Tools skill",align="center") %>%
  hc_add_theme(hc_theme_elementary())

hchart(na.omit(MOOCSkill),hcaes(x=JobSkillImportanceMOOC,y=count),type="pie",name="Count") %>% 
  hc_exporting(enabled = TRUE) %>%
  hc_title(text="Piechart of importance of MOOCs",align="center") %>%
  hc_add_theme(hc_theme_elementary())

hchart(na.omit(KaggleRankSkill),hcaes(x=JobSkillImportanceKaggleRanking,y=count),type="pie",name="Count") %>% 
  hc_exporting(enabled = TRUE) %>%
  hc_title(text="Piechart of importance of Kaggle Rankings",align="center") %>%
  hc_add_theme(hc_theme_elementary())









```

1. We can see from the above plot that the most unnecessary skill amongst all is having a knowledge of Enterprise tools, Degree, Kaggle Rankings and MOOCs. These have higher count of unnecessary skills entered by the participants.


2. Whereas, Knowledge of Statistics,Python,R and  Big data skills are most necessary and Nice to have skills as per answers entered by the survey participants.



-----------------------


### What proves that you have good Data science knowledge?


```{r}
knowlegdeDf<-SurveyDf %>% group_by(ProveKnowledgeSelect) %>%
  summarise(count=n()) %>%
  arrange(desc(count))

knowlegdeDf[1,]<-NA 

hchart(na.omit(knowlegdeDf),hcaes(x=ProveKnowledgeSelect,y=count),type="column",color="#049382",name="count") %>% 
  hc_exporting(enabled = TRUE) %>%
  hc_title(text="Barplot of what proves you have Datascience knowledge",align="center") %>%
  hc_add_theme(hc_theme_elementary())
  


```



Let's now heck the formal education of participants:

```{r}

table(FormalEducation)

```



------------------------


Let's check the most famous machine learning technique in which participants consider themselves competent?


```{r}
Mltechique<-SurveyDf %>% group_by(MLTechniquesSelect) %>%
  summarise(count=n()) %>% 
  arrange(desc(count)) %>%
  top_n(20)
  
Mltechique[1,]<-NA

hchart(na.omit(Mltechique),hcaes(x=MLTechniquesSelect,y=count),type="column",color="purple",name="count") %>% 
  hc_exporting(enabled = TRUE) %>%
  hc_title(text="Barplot of competent ML techniques of participants",align="center") %>%
  hc_add_theme(hc_theme_elementary())
  
  

```

So we cant notice that *Logistic regression, Decision trees, Random forets* are the top 2 most competent techniques in which the participants are competent and can successfully implement and are most efficient in implementing. 





-----------------------


###Let's check which Learning algorithm participants use at work ? 

Now we will check which machine learning algorithm is most used by the participants at their work.


```{r}

MLalgoWork<-SurveyDf %>% group_by(WorkAlgorithmsSelect) %>%
  summarise(count=n()) %>%
  arrange(desc(count)) %>%
  top_n(20)

MLalgoWork[c(1,3),]<-NA


hchart(na.omit(MLalgoWork),hcaes(x=WorkAlgorithmsSelect,y=count),type="column",color="green",name="count") %>% 
  hc_exporting(enabled = TRUE) %>%
  hc_title(text="Barplot of Most used ML algorithms at Work",align="center") %>%
  hc_add_theme(hc_theme_elementary())
  


```


> Again as we can see from the above plot, *Regression,Logistic regression and decision trees* lead the pack as the most used learning algorithms which used at work by participants.



----------------------


### Now let's check which tools are used most at work?

This field answers -For work, which data science/analytics tools, technologies, and languages the participants have used in the past year? 

We are going to find tht top 20 tools.


```{r}

ToolatWork<-SurveyDf %>% group_by(WorkToolsSelect) %>%
  summarise(count=n()) %>%
  arrange(desc(count)) %>%
  top_n(20)

ToolatWork[c(1),]<-NA


hchart(na.omit(ToolatWork),hcaes(x=WorkToolsSelect,y=count),type="column",color="#7C0E3E",name="count") %>% 
  hc_exporting(enabled = TRUE) %>%
  hc_title(text="Barplot of Most used data science tools used at Work",align="center") %>%
  hc_add_theme(hc_theme_elementary())

```

> From the above plot we can see that *Python and R are collectively used* by datascientists the most as entered by the survey participants. Hence Python and R still tops the most used tools at work according to the survey.



----------------------


### Most used ML method at work?


```{r}
MethodatWork<-SurveyDf %>% group_by(WorkMethodsSelect
) %>%
  summarise(count=n()) %>%
  arrange(desc(count)) %>%
  top_n(20)

MethodatWork[c(1,3),]<-NA


hchart(na.omit(MethodatWork),hcaes(x=WorkMethodsSelect
,y=count),type="column",color="#F14B5B",name="count") %>% 
  hc_exporting(enabled = TRUE) %>%
  hc_title(text="Barplot of Most used ML and DS methods used at Work",align="center") %>%
  hc_add_theme(hc_theme_elementary())



```



