---
title: "Analyzing Kaggle survey Data"
output: html_notebook
author: "Anish Singh Walia"
---

## AIM 

This is a data analytics project for mining analyzing, visualizing the data collected by the Kaggle Data science survey conducted in 2017.


### let's get started

#### Importing the dataset in R


```{r,message=FALSE,warning=FALSE}

require(data.table)
require(plotly)
require(ggplot2)
require(tidyverse)

SurveyDf<-fread("../Datasets/kagglesurvey2017/multipleChoiceResponses.csv") #for faster data reading

```


-------------------


### Exploratory data analysis


##### 1) Part 1- Analyzing country,ethnicity, gender,age,employment status, learning datascience and other related basic features of the survey participants.

Checking the distribution of each variable-
```{r,message=FALSE,warning=FALSE}

table(SurveyDf$GenderSelect)

table(SurveyDf$Country)

summary(na.omit(SurveyDf$Age))

table(SurveyDf$EmploymentStatus)


```


Let's visualize the above varibles to understand the distribution better
I will use the _plotly_ package.

```{r}

plot_ly(type="bar",x=SurveyDf$GenderSelect)

```


