---
title: "Analyzing Kaggle Data Science Survey Data-2017:PART-3"
author: "Anish Singh Walia"
output:
  html_document:
    df_print: paged
---


```{r,echo=FALSE,results='hide' ,message=FALSE, warning=FALSE, r,echo=FALSE, results='hide'}
require(data.table)
require(highcharter)
require(ggplot2)
require(tidyverse)

SurveyDf<-fread("../Datasets/kagglesurvey2017/multipleChoiceResponses.csv") #for faster data reading

attach(SurveyDf)
```




## AIM 

This is the part 3 of this project.This is a data analytics project for mining analyzing, visualizing the data collected by the Kaggle Data science survey conducted in 2017.



## 1) Part 3- This section will analyze and study the professional lives of the participants, their major degree ,time spend studying data science topics, what job titles they hold,which ML method they actually use in the industries , which bolgs the participants prefer the most for studying data science etc.



###Let's get started.

1) Let's start with the most preferred blog sites for learning datascience-This is a multiple answer field. Let's find the top 15 most preferred answers.

```{r message=FALSE, warning=FALSE}

blogs<-SurveyDf %>% group_by(BlogsPodcastsNewslettersSelect) %>%
  summarise(count=n()) %>% 
  top_n(15) %>% 
  arrange(desc(count))

#removing NA value
blogs[1,1]<-NA
colnames(blogs)<-c("Blogname","Count")

#let's plot them
hchart(na.omit(blogs),hcaes(x=Blogname,y=Count),type="column",color="#062D67") %>% 
  hc_exporting(enabled = TRUE) %>%
  hc_title(text="Barplot of most preferred blogs for learning",align="center") %>%
  hc_add_theme(hc_theme_elementary()) 



```
hence one can see that one of the most famous and preferred blog sites are __R bloggers and Kdnuggets__.





